Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2018-01-18 manuscript/Appendix5.Rmd
updates NDVI based analysis with table of posteriors

Our NDVI-model results are very similar to the ANPP-model results (Figure A5-1).
As with our ANPP-model results, the positive offset for the drought treatment does not result in a significantly different slope once applied to the control slope.

@@

@@

generated quantities{
  corr_matrix[Npreds2] R = multiply_lower_tri_self_transpose(L_u);
  cov_matrix[Npreds2] V = quad_form_diag(R,sigma_u);
}

```

>>>>

Our NDVI-model results are very similar to the ANPP-model results (Figure A5-1).
As with our ANPP-model results, the positive offset for the drought treatment does not result in a significantly different slope once applied to the control slope (Table A5-1).

@@

```{r effect_table, include=TRUE, comment=FALSE,warning=FALSE,message=FALSE,results='asis', echo=FALSE}
library(xtable)
treat_effects <- data.frame(extract(all_fit, pars = 'beta')) %>% 
  mutate(iteration = row_number()) %>% 
  gather(param_name, estimate, starts_with('beta')) %>%
  mutate(param_name = factor(param_name, labels = param_labels)) %>% 
  spread(param_name, estimate) %>% 
  mutate(`Drought::Intercept` = `Drought::Intercept` + `Control::Intercept`, 
         `Irrigation::Intercept` = `Irrigation::Intercept` + `Control::Intercept`,  
         `Drought::Slope` = `Drought::Slope` + `Control::Slope`, 
         `Irrigation::Slope` = `Irrigation::Slope` + `Control::Slope`) %>%
  gather(param_name, estimate, -iteration)

effect_summary <- treat_effects %>%
  group_by(param_name) %>%
  summarise(mean_estimate = round(mean(estimate), 2),
            median_estimate = round(median(estimate), 2),
            lower_95_ci = round(quantile(estimate, probs = c(0.025)), 2),
            upper_95_ci = round(quantile(estimate, probs = c(0.975)), 2)) %>%
  separate(param_name, into = c("Treatment", "Coefficient"), sep = "::") %>%
  arrange(Coefficient, Treatment) %>%
  select(Coefficient, everything())

colnames(effect_summary) <- c("Coefficient", "Treatment", "Posterior Mean", "Posterior Median",
                              "Lower 95\\% BCI", "Upper 95\\% BCI")
coef_caption <- "Summary statistics from the posterior distributions of coefficients for each treatment ($\\beta$ coefficients in equation 1). The `Intercept' and `Slope' summaries reported here for drought and irrigation are from the posterior distributions of the intercept and slope for the control treatment plus the offsets for each treatment. Posterior distributions of the offsets are in Figure A5-1."
print(xtable(effect_summary, caption = coef_caption, digits = 2),
      caption.placement="top",
      include.rownames = F,
      sanitize.colnames.function = identity,
      comment = FALSE,
      size = "normalsize")
```

@@

generated quantities{
  corr_matrix[Npreds2] R = multiply_lower_tri_self_transpose(L_u);
  cov_matrix[Npreds2] V = quad_form_diag(R,sigma_u);
}
```
